\chapter{Future Scope}
\section{User Interface}
{\normalsize The user interface is built in basic HTML, CSS and JavaScript in this prototype, this has to be built using another library called ReactJS for much more user friendly designs as well as better interactivity. \\[0.1in]
ReactJS recently became popular after Facebook used it for their frontend. The special thing about React is that instead of updating entire DOM every time something in the state of website changes, it just updates the specific node which updates. This ensures faster and optimized user interaction. As Mechanical Chef soughts to stream live video and cooking stream, faster UI is a must have. 
}
\section{Record a recipe}
{\normalsize The functionality for preparing a customized recipe and recording it in the database is a very complex problem yet to be solved. The recipes are encoded in three of the following steps for now : 
\begin{itemize}
    \item Heat
    \item Stir
    \item Drop
\end{itemize}
The procedure for preparing an algorithm from a recipe is a tedious task and requires a specialist to code all the steps into an Excel file which can be fed to the robot. This however is not possible for a user and thus a proper UI had to be developed for the same. Voice inputs are being considered a viable option.
}
\section{Hosting a Local Network on the Robot}
{\normalsize For users who do not have an access to the internet, a personal area network (maybe through bluetooth) can be hosted on the machine locally and can connect to the user for a quick preparation of dishes or for demonstration purposes. \\[0.1in]
For this personal area network a separate storage had to be embedded into the robot for making a public account and storing the user information on the server when it gets an access to the internet.
}
\section{User Login through OTP}
{\normalsize After a brainstorming session and weekly discussions we decided that the user registration process had to be kept much more simpler and quick for the comfort of the user.\\[0.1in]
This could be achieved by finding a faster way to register a user (even without internet access on a local network hosted on the machine) this could be made possible by registration using an OTP sent to the mobile number.
}
